\thispagestyle{fancy}
\renewcommand\abstractname{\zihao{-3} \TitleENG}
\phantomsection
\begin{abstract}
    \addcontentsline{toc}{section}{ABSTRACT}
    \zihao{5}
    \vspace{\baselineskip}

    \noindent{\bfseries \zihao{5} Abstract:}
% //TODO: ENG
    \par With the development of Internet technology, companies are now gradually transforming their management mode from the traditional closed type to the open type, which is called open source. Open source platform plays an important role in the field of software development, and it contribute to the transformation of traditional production methods. These transformation leads to a greater demand for the governance of open organizations and open source communities. Therefore, explaining the current situation of the open source community and promoting the improvement of the community mechanism has become a valuable research direction.

    \par Hypertrons is an open source RPA(Robotic Processing Automation) platform initiated by X-lab. While providing cross-platform interactive functions, it also collects open data from each platform as the basis of decision-making. These data effectively support the analysis of digital operations in open source communities. In this article, we will introduce the front-end extension of Hypertrons , which is a mini kanban for open organizations, aiming at better data visualization features.
    
    \par The mini kanban for open organizations is developed as a browser extension. It inserts visual components into web pages with specific URLs as well as provides interactive methods. As a result, it can provide effective monitoring and operational assistance for open organizations without the need to change user habits greatly. 
    \newline
    \newline
    {\bfseries \zihao{5} Keywords：} {\zihao{5} \KeywordsENG}
\end{abstract}